Compare NE-combined vs. NE-separated reference

### 2025-07-10 analyses/cell-type-neuroblastoma-04/exploratory-notebooks/separate-tumor.Rmd
update directories

module_dir <- file.path(repository_base, "analyses", "cell-type-neuroblastoma-04")
results_dir <- file.path(module_dir, "results", "singler")
data_dir <- file.path(repository_base, "data", "current", "SCPCP000004")
```

```{r file paths}
# SingleR results
combined_singler_file <- file.path(
  results_dir,
  params$sample_id,
  "aggregated",
  "NE-tumor-combined",
  glue::glue("{params$library_id}_singler-results.rds")
)

separated_singler_file <- file.path(
  results_dir,
  params$sample_id,
  "aggregated",
  "NE-tumor-separated",
  glue::glue("{params$library_id}_singler-results.rds")
)

>>>>

module_dir <- file.path(repository_base, "analyses", "cell-type-neuroblastoma-04")
results_dir <- file.path(module_dir, "results")
combined_results_dir <- file.path(results_dir, "singler-test_combined-tumor-ne")
separated_results_dir <- file.path(results_dir, "singler-test_separated-tumor-ne")
data_dir <- file.path(repository_base, "data", "current", "SCPCP000004")
```

```{r file paths}
# SingleR results
combined_singler_file <- file.path(
  combined_results_dir,
  params$sample_id,
  glue::glue("{params$library_id}_singler-results.rds")
)

separated_singler_file <- file.path(
  separated_results_dir,
  params$sample_id,
  glue::glue("{params$library_id}_singler-results.rds")
)
